---
title: "cm011"
author: "Cody"
date: "October 10, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(singer)
data("singer_locations")
View(singer_locations)
```
From last time we had,
```{r}
hfd_y <- singer_locations %>% 
  select(song_id,year,duration:artist_familiarity) %>% 
  gather(key="Measures",value="My_values",duration:artist_familiarity)

plot <- hfd_y %>% 
  filter(year>1950) %>% 
  ggplot(aes(x=year,y=My_values))+
  geom_point(alpha=.2,color="orange")+
  facet_wrap(~Measures,scales="free_y")

plot

```
We have plotted for each value, the duration, hottness and familiarity and had to fix the scales since the values were not on the same order.


```{r}
hfd_y %>% 
  spread(Measures,My_values)
```
If we want to recover the original dataset (before we gathered it into longer columns), we need to have some form of a unique identifier. In this case, we use "Song_id" to do this unique identification. You can also select the artist name, title .and the release to get this uniqueness (multiple columns can be used together to get uniqueness)

```{r}
library(reshape2)
hfd_y_mean <- hfd_y %>% 
              dcast(year ~ Measures, value.var = "My_values",
              fun.aggregate = mean, na.rm = TRUE)
View(hfd_y_mean)
```
Now we have taken the average of each the variables of interest per year. We could change the aggregated function to variance or even specify a different variable of interest, maybe per artist.

Similarly, we could use the group_by and summarize function to do something similar.

```{r}
typeof(plot)
class(plot)
typeof(`%>%`)
class(`%>%`)
```
