---
title: "cm103"
author: "Cody"
date: "October 31, 2017"
output: pdf_document
---

## Vectors
```{r}
v_log <- c(TRUE, FALSE, FALSE, TRUE)
v_int <- 1:10
v_double <- 1:4*2.1
v_char <- letters[1:4]
```
You can pull with vectors and drop terms with negatives
```{r}
v_char[v_log]
v_int[-5]
```
You will modify the entire vector's type if you modify a single entrie's type.
```{r}
v_double_copy <- v_double
v_double_copy[2] <- "uh oh"
str(v_double_copy)
```
## Lists

```{r}
x <- list(1:3,c("four","five"))
y <- list(logical = TRUE, integer = 4L, double = 4*1.2, character = "char")
z <- list(letters[26:22], transcendental = c(pi,exp(1)), f = function(x) x^2)

y[c(2,3)]
z[2]
z$transcendental
z['transcendental']
```
To extract, there are a few options, single brackets will retain the outer shell's structure, where double brackets will throw that away and keep the structure of only the inner
```{r}
y[2]
y[[2]]
```
## For loops

```{r}
n <- 5
res <- rep(NA_integer_,n)

for(i in seq_len(n)){
  res[i] <- i^2
}

res

(1:n)^2
```
Issue with lists and vectorizing though
```{r}
exp(v_double)
l_double <- as.list(v_double)
exp(l_double)
```
# Purr

```{r}
library(purrr)

map_dbl(l_double,exp)
```

```{r}
library(stringr)

# map_chr(fruit,str_split," ")

fruit %>% 
  map(str_split," ")

fruit %>% 
  map_chr(str_to_upper)
```

# Different section

```{r}
library(repurrrsive)
library(listviewer)
library(purrr)

str(gh_users)

jsonedit(gh_users)

map(gh_users,"login")

#It turns out the position for the login is 18
gh_users %>% 
  map(18)

map(gh_users, `[`, c("login", "name", "id", "location"))

map(gh_users, magrittr::extract, c("login","name"))
```

