---
title: "cm102"
author: "Cody"
date: "October 26, 2017"
output: pdf_document
---
 Some basic things,
 
```{r}
library(gapminder)
str(gapminder)
## get to know the functions mentioned above
min(gapminder$lifeExp)
max(gapminder$lifeExp)
range(gapminder$lifeExp)
max(gapminder$lifeExp) - min(gapminder$lifeExp)
with(gapminder, max(lifeExp) - min(lifeExp))
range(gapminder$lifeExp)[2] - range(gapminder$lifeExp)[1]
with(gapminder, range(lifeExp)[2] - range(lifeExp)[1])
diff(range(gapminder$lifeExp))
```

Building a function
```{r}
max_minus_min <- function(x) max(x) - min(x)
max_minus_min(gapminder$lifeExp)

max_minus_min(1:10)
max_minus_min(runif(1000))
```
It makes sense to build in error codes to identify the issues or stop if something shouldn't work.
```{r}
mmm <- function(x) {
  stopifnot(is.numeric(x))
  max(x) - min(x)
}
mmm(gapminder)
```
A more sophisticated error message,
```{r}
mmm2 <- function(x) {
  if(!is.numeric(x)) {
    stop('I am so sorry, but this function only works for numeric input!\n',
         'You have provided an object of class: ', class(x)[1])
  }
  max(x) - min(x)
}
mmm2(gapminder)
```
Example: Take a number and return it mod 10.
```{r}
mod_10 <- function(x) {
  if(!is.numeric(x)) {
    stop('This function is of class: ', class(x)[1])
  }
  x%%10
}
mod_10(1001)
mod_10('Hi')
```
Now lets look at quantiles
```{r}
quantile(gapminder$lifeExp)
quantile(gapminder$lifeExp, probs = 0.49)

the_probs <- c(0.25, 0.75)
the_quantiles <- quantile(gapminder$lifeExp, probs = the_probs)
max(the_quantiles) - min(the_quantiles)
```
So then writing a function that bases itself on quantiles,
```{r}
qdiff1 <- function(x, probs) {
  stopifnot(is.numeric(x))
  the_quantiles <- quantile(x = x, probs = probs)
  max(the_quantiles) - min(the_quantiles)
}
qdiff1(gapminder$lifeExp, probs = c(0.25, 0.75))
IQR(gapminder$lifeExp)
```
Specifying default values,
```{r}
qdiff2 <- function(x, probs = c(0, 1)) {
  stopifnot(is.numeric(x))
  the_quantiles <- quantile(x, probs)
  return(max(the_quantiles) - min(the_quantiles))
}
qdiff2(gapminder$lifeExp)
```
A more general modulus function which actually saves the output by names that can be called,
```{r}
mod_x <- function(value,x=10) {
  stopifnot(!is.integer(value)&&!is.integer(x))
  int = value%/%x
  mod = value%%x
  output <- list(quotient=int,remainder=mod)
  return(output)
}
mod_x(10,3)
mod_x(10,'Hi')
mod_x('Hi',10)
```
Now lets deal with NAs
```{r}
z <- gapminder$lifeExp
z[3] <- NA
quantile(gapminder$lifeExp)
quantile(z)
quantile(z,na.rm=1)

qdiff3 <- function(x, probs = c(0, 1),na=FALSE) {
  stopifnot(is.numeric(x))
  the_quantiles <- quantile(x, probs, na.rm = na)
  return(max(the_quantiles) - min(the_quantiles))
}
qdiff3(z,na=TRUE)
```
Now lets deal with the ... arguement
```{r}
qdiff4 <- function(x, probs = c(0, 1), na.rm = TRUE, ...) {
  the_quantiles <- quantile(x = x, probs = probs, na.rm = na.rm, ...)
  return(max(the_quantiles) - min(the_quantiles))
}
set.seed(1234)
z <- rnorm(10)
quantile(z, type = 1)
quantile(z, type = 4)
all.equal(quantile(z, type = 1), quantile(z, type = 4))
qdiff4(z, probs = c(0.25, 0.75), type = 1)
```
So above, we have that even though 'type' is not a variable defined explicitely in our function, it is implicitely defined because the quantile function we use has a set of masked variables that we are now accessing.

Now work on testing functions
```{r}

library(testthat)
test_that('invalid args are detected', {
  expect_error(qdiff4("eggplants are purple"))
  expect_error(qdiff4(iris))
  })
test_that('NA handling works', {
  expect_error(qdiff4(c(1:5, NA), na.rm = FALSE))
  expect_equal(qdiff4(c(1:5, NA)), 4)
})

qdiff_no_NA <- function(x, probs = c(0, 1)) {
  the_quantiles <- quantile(x = x, probs = probs)
  return(max(the_quantiles) - min(the_quantiles))
}
test_that('NA handling works', {
  expect_that(qdiff_no_NA(c(1:5, NA)), equals(4))
})
```

