---
title: "Untitled"
author: "Cody"
date: "November 2, 2017"
output: pdf_document
---

## Picking up directly from cm103:

```{r}
library(tidyverse)
library(purrr)
library(repurrrsive)
```
The gh_repos data set is very nested and this makes it difficult to access the varying components.
```{r}
data("gh_repos") #Store the data but as a "promise", meaning R is aware of its presence but its too big

gh_repos #Even writing this will now load the dataset and we see its very big.

View(gh_users) #Need to update r studio, View isn't working

library(listviewer)
jsonedit(gh_repos) #Alternatively
```
Extracting information from lists: Pull from the first level the full names.
```{r}
gh_repos %>% 
  map_chr(list(1,"full_name"))
```

```{r}
gh_repos %>% 
  map_int(list(4,"owner","id"))
```
Want to make a named data frame based on pulling entries out of another data frame?
We will take the first repos owner id and create a names vector, put them together to be a two column dataframe
```{r}
library(tibble)
u_id <- gh_repos %>% 
  map_int(list(1,"owner","id"))

gh_repos_named <- gh_repos %>% 
  set_names(u_id)

gh_repos_df <- gh_repos_named %>% 
  enframe("user_id", "repository stuff")

jsonedit(gh_repos_df)
```
Instead we will use logins instead of id
```{r}
u_login <- gh_repos %>% 
  map_chr(list(1,"owner","login"))

gh_repos_named <- gh_repos %>% 
  set_names(u_login)

gh_repos_df <- gh_repos_named %>% 
  enframe("user_login", "other repository stuff")

jsonedit(gh_repos_df)
```
```{r}
gh_repos_df %>%
  filter(user_login %in% c("masalmon", "leeper")) %>% 
  mutate(number_of_repositories=map_int(`other repository stuff`,length)) %>% 
  jsonedit()
```
Put together the aliases and the names of each character on GoT
```{r}
aliases_names <- set_names(map(got_chars,"aliases"),map(got_chars,"name"))
map_int(aliases_names,length) #Lol Dany has 11 names

collapse_by_comma <- function(vec_of_strings){
  paste(vec_of_strings,collapse = ", ")
}
map(aliases_names,collapse_by_comma)
```

