---
title: "cm107"
author: "Cody"
date: "November 14, 2017"
output: pdf_document
---
# 11/14

Here is an example of using remake to do all the generation of plots and loading data. This requires the following files in the directory:

* 00_download-data.R
* 01_filter-reorder-plot.R
* 02_aggregate-plot.R

```{r}
## one script to rule them all

## clean out any previous work
outputs <- c("lotr_raw.tsv",                     # 00_download-data.R
	     "lotr_clean.tsv",                   # 01_filter-reorder-plot.R
	     "total-words-by-film-race.tsv",     # 02_aggregate-plot.R
             list.files(pattern = "*.png$"))
file.remove(outputs)

## run my scripts
source("00_download-data.R")
source("01_filter-reorder-plot.R")
source("02_aggregate-plot.R")
```

# Here is material from today:

This is cool! Here is some info on how to create shiny apps:
* [Interactive tutorial](https://docs.google.com/presentation/d/1dXhqqsD7dPOOdcC5Y7RW--dEU7UfU52qlb0YD3kKeLw/edit#slide=id.gd53c66aaf_0_1)
* [Example github repo](https://github.com/sdasadia/Global-Terrorism-Database)
* [Example app](https://sarthakdasadia.shinyapps.io/GlobalTerrorism/)
* [Class tutorial](http://stat545.com/shiny01_activity.html)

To actually create these apps:
```{r}
install.packages("shiny")
```

This will start a server for an example, the url provided can actually be googled and seen by anyone.
```{r}
library(shiny)
runExample("01_hello")
```

Here I create my own app! See folder: First_shiny

**Note:** It is important that the shiny app is in a seperate location with only necessary files with it.



